\huge Tor's Usability for Censorship Circumvention

### 2016-04-18 pets2017-paper/pets2017-paper.tex
add conclusion sections (and mess around with formatting)

\begin{figure*}[t]
	\centering
		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
		\caption{In the ``OLD'' interface, users are asked, ``Does your Internet Service Provide (ISP) block or 
		otherwise censor connections to the Tor Network?'' (B1). A ``Yes'' determines that a bridge should 
		be configured and directs to the bridge configuration screen (B2). 
		The ``NEW'' interface gives users advice on configuring bridges
		while giving the option of not configuring a bridge, on one screen (B).} 
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
		\caption{In the ``OLD'' interface, users are asked, ``Does this computer need a local proxy to connect
		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
		proxy configuration screen (P2). The ``NEW'' interface checks the local machine's proxy settings,
		and informs the user whether a proxy is required, and if so, what those settings are (P).}
\end{figure*}

@@

@@

\section {Acknowledgments}
{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabela Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.} 
{\color {red} Tor Browser devs for taking our recommendations to heart and implementing changes.}

\section{Conclusion} 
{\color {red} I am a fan of not having long, rambling conclusions. I leave
that for the discussion section. This section is more of a courtesy to the 
people who read the abstract, look at the figures, and then read the 
conclusion. Think of something to tell those people here. Something along
the lines of a tl;dr summary of the paper.}

>>>>

@@

 \begin{figure*}[h]
	\centering
		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
		\caption{In the ``OLD'' interface, users are asked, ``Does your Internet Service Provide (ISP) block or 
		otherwise censor connections to the Tor Network?'' (B1). A ``Yes'' determines that a bridge should 
		be configured and directs to the bridge configuration screen (B2). 
		The ``NEW'' interface gives users advice on configuring bridges
		while giving the option of not configuring a bridge, on one screen (B).} 
\end{figure*}

\begin{figure*}[h]
	\centering
		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
		\caption{In the ``OLD'' interface, users are asked, ``Does this computer need a local proxy to connect
		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
		proxy configuration screen (P2). The ``NEW'' interface checks the local machine's proxy settings,
		and informs the user whether a proxy is required, and if so, what those settings are (P).}
\end{figure*}

@@

%\section {Acknowledgments}
%{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabela Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.} 
%{\color {red} Tor Browser devs for taking our recommendations to heart and implementing changes.}

\section{Conclusion} 
We conducted a series of experiments to improve the Tor launcher configuration interface, which helps users circumvent censorship using Tor Browser. The qualitative user study interviews a screened 16 participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common struggles, such as difficulty in answering technical questions, feeling unqualified to make technical choices, and not receiving feedback in the event of a failed configuration. This feedback is used to guide the redesign of the configuration interface.

We test the impact of our changes on 124 participants in the quantitative user study to find that that the changes made cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates. We observe and quantify common behavioral trends based on logs and video recordings of our participants, and offer recommendations that we believe will greatly increase the success rate and time to success for future users.
